---
title: "Alcohol vs Seat choice"
author: "Esteffani Maldonado"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
Viewing this boxplot, we can see that the 75th percentile of people who sit in the back is way higher than both the front area and the middle area. The median amounts of alcohol for the front-seat students and middle-seat students are about 0 and 1, respectively. The median for the back-seat students is about 5. Based on these observations, we can assume that students who sit closer to the back drink more than students who sit towards the front.   
    
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

In this fancy box plot, we can see that the median amount of alcohol is still higher in the back section than it is in the middle or front section. However, we can see that the boxes on this plot contain notches towards the center where the median is located. This is an indication of the standard deviation. There is a wider standard deviation in the back seat section compared to the standard deviation for the front seat section and the standard deviation for the middle seat section. This supports our earlier claim, but this also supports the new idea that there is more variation in the back than there is in the front and the middle.   
  
## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
  
Here we can see the exact numbers that correspond with our box plots above. The mean amount of alcohol that the back-seat students drink is 9.6, while the mean amount of alcohol that the middle-seat students drink is about 3.3, and the mean amount that the front-seat students drink is 1.8. The standard deviation(sd) for the back-seat students is almost 13, while the sd for the front-seat students is 3.9, and the sd for the back-seat students is 6.4. So, we can see that these numbers agree with both of our claims that the back seat students drink more than the front and middle seat students, but there is also more variation in the back-seat data than for the front-seat and middle-seat.
  
## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

My p-value from the anova test is 0.000116. That means that there is at least two rows in the data where the amount of alcohol is statistically different. If the null hypothesis were true, then there is a 0.000116% chance that there are two rows with significant difference in alcohol consumption. To find which rows are different, we will run a TukeyHSD test.

```{r}
plot(TukeyHSD(model1))
```
  
If you look at the front compared to the back, the differences in the mean level of drinking appear to be between 4-12 drinks more than the front. The back section appears to be drinking 10-3 drinks more than the middle. There doesn't appear to be any difference in the middle and front mean level, and we can see this because 0 is found within the confidence interval.   
  
## Conclusions
  
To begin, we interpreted the problem in order to find which helper file we needed. This was a Numerical~Categorical problem, so we uploaded the appropriate helper file of the same name. We observed the given plots, and based on the plots, we concluded that the back row drinks more alcohol on average than the front and middle rows, and we found that there is more variation in the back row while the middle and front rows did not have as much variation compared to each other. Our claims were cemented when we performed the TukeyHSD test, which display the mean differences of each row compared to each other.  
  